A Strategy-Proof Budget Feasible Online Mechanism for Crowdsensing with Time-Discounting Values

### 2016-12-05 paper.tex
tmc

% \documentclass[conference,letterpaper,10pt]{IEEEtran}
\documentclass[10pt,journal,letterpaper,compsoc]{IEEEtran}
\makeatletter
\def\ps@headings{%
\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}%
\def\@oddfoot{}%
\def\@evenfoot{}}
\makeatother
\IEEEoverridecommandlockouts
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{listings}

%\usepackage{algorithm}
%\usepackage{algorithmicx}
\usepackage[vlined,ruled,commentsnumbered,linesnumbered]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{amsmath,amsthm,amsfonts,amssymb,bm}
\usepackage{comment}
\usepackage{subfigure}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{flushend}
\usepackage{epstopdf}

\usepackage{bbding}

@@

%\title{A Strategy-Proof and Budget Feasible Online Crowdsensing Mechanism Design with \\Time-Discounting Value}
\title{\huge{A Strategy-Proof Budget Feasible Online Mechanism for Crowdsensing with Time-Discounting Values}}
\author{
Jiapeng Xie, Shuo Yang, Fan Wu,  Xiaofeng Gao, and Guihai Chen\\
Shanghai Key Laboratory of Scalable Computing and Systems\\
Shanghai Jiao Tong University, China\\
\{xjpsjtu, wnmmxy\}@sjtu.edu.cn; \{fwu, gao-xf, gchen\}@cs.sjtu.edu.cn
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem J. Xie, F. Wu, and G. Chen are with the Department of Computer Science and Engineering, Shanghai Key Laboratory of Scalable Computing and Systems, Shanghai Jiao Tong University, Shanghai 200240, P.R. China.
Emails: xjpsjtu@sjtu.edu.cn, \{fwu, gchen\}@cs.sjtu.edu.cn.
\IEEEcompsocthanksitem F. Wu is the corresponding author.
\IEEEcompsocthanksitem This work was supported in part by the State Key Development Program for Basic Research of China (973 project 2014CB340303), in part by China NSF grant 61422208, 61472252, 61272443 and 61133006, in part by Shanghai Science and Technology fund 15220721300, in part by CCF-Tencent Open Fund, and in part by the Scientific Research Foundation for the Returned Overseas Chinese Scholars. The opinions, findings, conclusions, and recommendations expressed in this paper are those of the authors and do not necessarily reflect the views of the funding agencies or the government.}
}

@@

However, a well running crowdsensing application needs massive data contributed by the participants to ensure the service quality~\cite{Wang:2015:CQO:2750858.2807513,Han:2016:PPR:2942358.2942385}. Since participating in crowdsensing tasks requires the participants to devote resource consumptions of their smartphones, participants are usually reluctant to share their sensing capabilities(\eg, \cite{Kawajiri:2014:SCI:2632048.2636064,Fan:2015:PTT:2789168.2795179,Karaliopoulos:2016:FLE:2942358.2942369}. Thus, it is necessary to design an incentive mechanism to compensate the participants. According to different settings of scenarios, two cases are often discussed, \ie, offline setting and online setting. Researches on incentive mechanism designs, such as~\cite{yang2012crowdsourcing,koutsopoulos2013optimal}, are usually based on offline scenarios, where participants are present simultaneously while the online scenarios are more common in practice, where participants arrive and leave dynamically. Designing an incentive mechanism in online scenarios is much more complicated, due to the lack of future information. Besides, it brings challenges in the realization of strategy-proofness, since participants may misreport their arrival or departure time in order to gain higher benefits. Here, intuitively, strategy-proofness means that one can maximize her benefit by truthfully revealing her private information (\eg, arrival time, departure time, or sensing cost).

@@

We note that most existing works on online mechanism design only consider flat values, \ie, the value of each participant's contributed data is fixed during her presence. However, in many time sensitive applications (\eg, real-time traffic or noise monitoring~\cite{Chon:2014:SWP:2632048.2636066,Ji:2016:USB:2971648.2971735,Zappatore:2016:CAM:2851613.2851699,Cherian:2015:PPG:2809695.2817881}), the participants usually have time-discounting values, \ie, the value of each participant's contribution decreases as time goes by~\cite{babaioff2009secretary, wu2014strategy}. The time-discounting property really complicates the mechanism design problem. For instance, it has been proved that no online algorithm can achieve a competitive ratio better than $\Omega(\textrm{log}n/\textrm{log}\,\textrm{log}n)$ for discounted secretary problem~\cite{babaioff2009secretary}. The time-discounting property of values will bring much more difficulty, especially on the strategy-proofness. In the most of the incentive mechanisms designed for online crowdsensing, the payment to a selected participant is based on her contributation. If she can cheat her type, such as arrival time or cost, she may be selected at different time. If this time is earlier than the time with truely report information, the value of this participant calculated by the platform will be higher than the true value. For the purpose of more reward, the participant may have more incentives to bid mendaciously.

@@

To address these challenges, we propose a budget feasible online incentive mechanism with time-discounting values. We first consider the case where the total value is the summation of each participant's value. We define the efficiency of a participant as her value divided by her cost. Since participants arrive dynamically, we take advantage of the efficiency information of those who have arrived (we call a sample set) to calculate a threshold, and use it to guide subsequent selections. The intuition of our design is to greedily choose participants with the highest efficiencies from the sample set, and calculate their average efficiency multiplying an increasing factor as a threshold. The increasing factor is used to prevent the participants from misreporting their arrival or departure time. We divide the total time into slots. At each time slot, we select participants with efficiencies higher than the threshold within the budget constraint, and then calculate their payments. The payment scheme is carefully designed to ensure strategy-proofness and individual rationality. We prove that our mechanism can achieve a constant competitive ratio compared with the optimal solution with full information. We next consider the case where the total value is a submodular function of the selected participants, which is a more general situation. We prove that the time and cost-truthfullness can still be guaranteed by the newly designed algorithms. The numerical results show that our proposed approach has superior performance to our benchmark mechanisms.
\subsection{Key Contributions}
The main contributions of this paper is listed as follows
\begin{itemize}
\item We design an online incentive mechanism for crowdsensing. In this process, participants arrive over time. Our mechanism is designed to take advange of their efficiency to select them and give them a payment.

\item As far as we know, we are the first to consider the time-discounting property of values. To address the potential new difficulty, we design a novel algorithm to calcuate a time-related threshold to select participants and determine their payment.

\item We think about two cases according to the value function. The value function in these two cases is linear additive and submodular, the latter is more general.
\end{itemize}
\subsection{Paper Organization}
The rest of the paper is organized as follows. We briefly review the related work in Section II. In Section III, We introduce the model of the budget feasible online mechanism problem with time-discounting values, and recall some important solution concepts. In Section IV, we present our design of a strategy-proof online  mechanism where the value function is the summation of each participant's value. In Section V, we consider the case where the value function submodular. In Section VI, we implement and evaluate our mechanism. Finally, we conclude this paper in Section VI.
%**********************************************************
%The key challenges in a budget feasible auction are how to persue the maximum value and balance incentive compatibility and the budget constraint. It gets harder when the participants arrive dynamicly. What is noticeable is that in existing works, the value of a specific participant is often fixed, \ie, the participant has a bid of uniform value during her presence in the auction, independent of when she is selected. But in some realms, such as applications intending to collect data by crowdsensng, which are always modeled as reverse auctions, the values of participants' contributed information decrease with time. The time discounting characteristic can make the problem more difficult. In this paper, we study a type of online reverse auction, where the participants compete to provide items or services with certain time discounting values. Then the provider gives some payment to the selected participants according to their bids. The objective is to obtain  the maximum total value and achieve strategy-proofness under a limited budget. It should be noted that for general utility functions, there is no truthful mechanism achieving a reasonable approximation ratio~\cite{singer2014budget}. In our paper, the total value of participants is simplified to the summation of their values at when they are selected.
%**********************************************************
%We present a formal methonology based on the mechanism design as an inventive method in the realm of crowdsensing. which is a new paradigm of applications that includes a platform and ubiquitous participants who hold mobile devices equipped with enhanced sensors~\cite{ganti2011mobile}. The platform recruits participants to upload sensing data and then compensate them some payment according to their value. It is always modeled as a reverse auction. When designing an incentive mechanism for crowdsensing, participants' value is often taken into account when determining the task allocation and the payment. But in existing work, this value of a specific participant is often fixed, \ie, the participants have a bid of uniform value to the platform during their presences in the auction. However in many crowdsensing applications, the value of participants is time discounting, decreasing with time in majority situations. Therefore in this paper, we consider a scenario, in which participants compete for being allocated tasks and then compensated some monetary payment, but her bidding value is changing over time.  The bid of each participant is her arrival time, departure time, her cost and value to the platform which diminishes with time. The objective is to design a strategy-proof mechanism and maximize the platform's gainning value with limited budget with respect to not only the time discounting values, but also the present time and cost of the participants.

@@

In the case where the value of a participant has nothing to do others', the total is the summeration of each participant's value. The type of each participant $i$ is $\theta_i=(a_i,d_i,v_i,c_i)$, where $a_i$ and $d_i$ represent her arrival and departure time respectively, $v_i$ denotes participant $i$'s value to the crowdsensing platform and $c_i$ represents her cost or reserve price in performing the sensing task. Here, reserve price is the minimum payment that a participant is willing to receive. In other words, each selected participant should get a payment no less than her reserve price. We note that $a_i$, $d_i$ and $c_i$ are participant $i$'s private information that are unknown to the service provider unless being reported, while $v_i$ is assumed to be $i$'s public information since participants' values can be known a prior or evaluated by the service provider \cite{peng2015pay,jin2015quality}. Upon participant $i$'s arrival, she will submit her bid $\hat{\theta}_i=(\hat{a}_i,\hat{d}_i,v_i,b_i)$ to the service provider. We note that since the participants are rational and selfish, they may cheat their arrival time, departure time, or reserve prices for the purpose of earning more payment or improving the possibility to be selected \cite{nisan2007algorithmic}, indicating that participant $i$'s bid may not be her true type. It is known that reporting earlier arrival or later departure can be prevented by heart-beat scheme~\cite{nisan2007algorithmic}, we focus on the scenario where each participant can only report an arrival time later than her true arrival time or a departure time earlier than her true departure time, \ie, $\hat{a}_i\ge a_i, \hat{d}_i\le d_i$. Participant $i$ can also misreport her reserve price $b_i \neq c_i$ to manipulate the participant selection process.

@@

\section{Mechanism Design}

In this section, we propose an online mechanism, which is named as TDM, satisfying the following properties:
\begin{itemize}
\item \textbf{Computational Efficiency}: Each step of the mechanism should be computed in polynomial time.

@@

\item \textbf{Competitive Efficiency}: We define the competitive ratio as the ratio between the expected total value gained in our mechanism and the optimal value where this provider has full information of all participants~\cite{zhao2014crowdsource}. We will prove our mechanism can achieve a constant competitive ratio. In our proof, we ignore the effect of time-discounting property because it will only change the constant coefficient.
\end{itemize}

@@

\begin{algorithm}
\BlankLine
\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output}
\caption{Modified greedy algorithm}
\label{alg:greedy}
\begin{small}
\Input{Budget $B$, the participant set $\mathbb{P}=\{p_1,p_2,...,p_n\}$}
\Output{Selected Participants}
\BlankLine
$\mathbb{S}\rightarrow\emptyset,C\rightarrow 0,\mathbb{U}\rightarrow\mathbb{S}$;\\
\While{$\mathbb{U}\neq\emptyset$}{
	select $p_i \in mathbb{U}$ that maximizes $\frac{v_i}{c_i}$;\\
	\If{$C+c_i\le B$}{
		$\mathbb{S}\rightarrow\mathbb{S}\cup{p_i}$;\\
		$C\rightarrow C+c_i$;\\
	}
	$\mathbb{U}\rightarrow\mathbb{U}\backslash\{p_i\}$;
}
Select a participant $p*$ that maximizes $v*$ over $\mathbb{P}$;\\
If $V(\mathbb{S})\ge v*$, output $\mathbb{S}$, otherwise, output $\{p*\}$;
\end{small}
\end{algorithm}

@@

When $\epsilon$ is sufficiently small, we can always find such a parameter $\lambda$ equals $2\left(\frac{U}{L}\right)^{l-1}$. Then the expected competitive ratio is:
\begin{align}
\left(\frac{U}{L}\right)^{2-2l}\frac{U}{16(U+L)}(1-\frac{1}{e}). 
\end{align}
\end{proof}
% Due to limitations of space, we omit the proof here.
%\begin{equation}
%\left\{
%\begin{aligned}
%\frac{\left(\frac{U}{L}\right)^{l-1}}{\lambda}<\frac{1}{2}\\
%\lambda < \frac{\left(\frac{U}{L}\right)^{l-2}}{\epsilon}\\
%\end{aligned}
%\right.
%\end{equation}
\section{Mechanism with Monotone Submodular Value Function}
In this section, we propose an online mechanism, which is named as TDMS, for the general model.
\subsection{System Model}
The general model is similar with the model we have presented in section III. However the task is divided into some sub-tasks and the bid of each participant includes the set of sub-tasks she can finish. The bid of of participant $i$ is $\theta_i=(a_i,d_i,p_i,c_i)$, where we use the same notation $p_i$ to represent the sub-task set of participant $p_i$ for brevity.
\subsection{Mechanism Design}
In last section, we propose an incentive mechanism for online crowdsensing with time-discounting values, specifically the total obtained value is linear summeration of value contributed by each participant, \ie,
%\begin{small}
\begin{equation}
V=\sum\limits_{i \in \mathbb{S}}v_i(t_i)
\end{equation}
%\end{small}
However in many scenarios~\cite{zhao2014crowdsource}, the value of participants to the platform is $f(\mathbb{S})$, where $f$ is a monotone submodular function ans $\mathbb{S}$ is the selected participants set. Particularly, we have solved the case where the value function $f(\mathbb{S})=\sum\limits_{i \in \mathbb{S}}v_i(t_i)$. Here we give the definition of monotone submodular function.
\begin{definition}[Monotone Submodular Function]
A function $f:2^{[n]}\to \mathbb{R}$ is submodular if and only if:
\begin{equation}
f(\mathbb{A}\cup\{i\})-f(\mathbb{A})\ge f(\mathbb{B}\cup \{i\})-f(\mathbb{B}). \quad \forall \mathbb{A}\subseteq\mathbb{B} \notag
\end{equation}
\end{definition}
In existing works focused on submodular function maximation in the realm of incentive mechanism design for crowdsensing, the marginal value contributed by a participant is related to the order she is selected. Besides, the total value is only decided by the tasks of the selected participants. However in this paper, considering the time-discounting property, the value function is a bit more complicated. We still use the notation $f$ to denote the value function without considering time-discounting value. When a participant $i$ is selected at time $t_i$, her marginal contribution given a subset $\mathbb{S}$ is $f_{i|\mathbb{S}}=(f(\mathbb{S}\cup\{i\})-f(\mathbb{S}))\times\beta ^{-t_i}$.
Assume the selected participant set is $\{i_1,i_2,...,i_n\}$ and their selected time is $t_{i_1},t_{i_2},...,t_{i_n}$ respectively. So when selecting the first participant $i_1$, her real contribution value is $f_{t_{i_1}}(\{i_1\})=f(\{i_1\})\times \beta^{-t_{i_1}}$. The value contributed by the secondly selected participant without consider time-discounting property is $f(\{i_1,i_2\})-f(\{i_1\})$ and her true contribution should be discounted by timing $\beta^{t_{i_2}}$. Thus, the total value contributed these two participants is $f_{t_{i_1},t_{i_2}}(\{i_1,i_2\}) = f_{t_{i_1}}(\{i_1\})\times \beta^{-t_{i_1}} + [f(\{i_1,i_2\})-f(\{i_1\})]\times\beta^{-t_{i_1}}$. We use $\tilde{f}$ to substitute $f$ when considering time-discounting property. So, the total value contributed by all these $n$ participants are
\begin{align}
&\tilde{f}(\{i_1,i_2,...,i_n\}) = f_{t_{i_1},t_{i_2},...,t_{i_n}}(\{i_1,i_2,...,i_n\}) \notag \\
&=f_{t_{i_1}}(\{i_1\})\times \beta^{-t_{i_1}} + [f(\{i_1,i_2\})-f(\{i_1\})]\times\beta^{-t_{i_1}} \notag\\
&+... +[f(\{i_1,i_2,...,i_{n}\})-f(\{i_1,i_2,...,i_{n-1}\})]\times\beta^{-t_{i_n}} 
\end{align}

\begin{theorem}
The new total value function $\tilde{f}$ with time-discounting value is monotone submodular.
\end{theorem}
\begin{proof}
We can prove this according to the definition of submodular function.

@@

We denote participant $i$'s marginal contribution given a subset $\mathbb{A}$ as
 $\tilde{f}^i_{t_i}(\mathbb{A}) = [f(\mathbb{A}\cup\{i\}) - f(\mathbb{A})]\times \beta^{-t_i}$.
Next we modify the procedure to calculate the threshold when the value function is submodular. Recall that we assume $L\le\frac{v}{b}\le U$ before, here we make a reasonable assumption that $L\le\frac{f^i(\emptyset)}{b_i}\le U$. Then we also can infer that $L\le\frac{f^i(\mathbb{A})}{b_i}\le U$ for all set $\mathbb{A}$

@@

Next we propose the participant selection algorithm as before. We should pay more attention to the truthfulness. Since the value function is submodular, the marginal distribution is related to a given subset. If the order of selection is changed, the marginal distribution will change as well. This is a new kind of opportunity for the participants to cheat her bids. Singer has ever studied a budget mechanism~\cite{singer2010budget}, where the value function is submodular. However it is used in offline scenario, we will give an online version.

>>>>

% \documentclass[conference,letterpaper,10pt]{IEEEtran}
\documentclass[10pt,journal,letterpaper,compsoc]{IEEEtran}
\makeatletter
\def\ps@headings{%
\def\@oddhead{\mbox{}\scriptsize\rightmark \hfil \thepage}%
\def\@evenhead{\scriptsize\thepage \hfil \leftmark\mbox{}}%
\def\@oddfoot{}%
\def\@evenfoot{}}
\makeatother
\IEEEoverridecommandlockouts
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{listings}
\usepackage{latexsym}
\usepackage[cmex10]{amsmath}
%\usepackage{algorithm}
%\usepackage{algorithmicx}
\usepackage[vlined,ruled,commentsnumbered,linesnumbered]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{amsmath,amsthm,amsfonts,amssymb,bm}
\usepackage{comment}
\usepackage{subfigure}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{flushend}
\usepackage{epstopdf}
\usepackage{textcomp}
\usepackage{bbding}

\hyphenation{op-tical net-works semi-conduc-tor}

@@

%\title{A Strategy-Proof and Budget Feasible Online Crowdsensing Mechanism Design with \\Time-Discounting Value}
\title{A Strategy-Proof Budget Feasible Online Mechanism for Crowdsensing with Time-Discounting Values}
\author{
Jiapeng Xie, Shuo Yang, Fan Wu,  Xiaofeng Gao, and Guihai Chen\\
Shanghai Key Laboratory of Scalable Computing and Systems\\
Shanghai Jiao Tong University, China
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem J. Xie, S. Yang, F. Wu, X. Gao and G. Chen are with the Department of Computer Science and Engineering, Shanghai Key Laboratory of Scalable Computing and Systems, Shanghai Jiao Tong University, Shanghai 200240, P.R. China.
Emails: \{xjpsjtu, wnmmxy\}@sjtu.edu.cn, \{fwu, gao-xf, gchen\}@cs.sjtu.edu.cn.
\IEEEcompsocthanksitem F. Wu is the corresponding author.
\IEEEcompsocthanksitem This work was supported in part by the State Key Development Program for Basic Research of China (973 project 2014CB340303), in part by China NSF grant 61422208, 61472252, 61272443 and 61133006, in part by Shanghai Science and Technology fund 15220721300, in part by CCF-Tencent Open Fund, and in part by the Scientific Research Foundation for the Returned Overseas Chinese Scholars. The opinions, findings, conclusions, and recommendations expressed in this paper are those of the authors and do not necessarily reflect the views of the funding agencies or the government.}
}

@@

However, a well running crowdsensing application needs massive data contributed by the participants to ensure the service quality~\cite{Wang:2015:CQO:2750858.2807513,Han:2016:PPR:2942358.2942385}. Since participating in crowdsensing tasks requires the participants to devote resource consumptions of their smartphones, participants are usually reluctant to share their sensing capabilities(\eg, \cite{Kawajiri:2014:SCI:2632048.2636064,Fan:2015:PTT:2789168.2795179,Karaliopoulos:2016:FLE:2942358.2942369}). Thus, it is necessary to design an incentive mechanism to compensate the participants. According to different settings of scenarios, two cases are often discussed, \ie, offline setting and online setting. Researches on incentive mechanism designs, such as~\cite{yang2012crowdsourcing,koutsopoulos2013optimal}, are usually based on offline scenarios, where participants are present simultaneously while the online scenarios are more common in practice, where participants arrive and leave dynamically. Designing an incentive mechanism in online scenarios is much more complicated, due to the lack of future information. Besides, it brings challenges in the realization of strategy-proofness, since participants may misreport their arrival or departure time in order to gain higher benefits. Here, intuitively, strategy-proofness means that one can maximize her benefit by truthfully revealing her private information (\eg, arrival time, departure time, or sensing cost).

@@

We note that most existing works on online mechanism design only consider flat values, \ie, the value of each participant's contributed data is fixed during her presence. However, in many time sensitive applications (\eg, real-time traffic or noise monitoring~\cite{Chon:2014:SWP:2632048.2636066,Ji:2016:USB:2971648.2971735,Zappatore:2016:CAM:2851613.2851699,Cherian:2015:PPG:2809695.2817881}), the participants usually have time-discounting values, \ie, the value of each participant's contribution decreases as time goes by~\cite{babaioff2009secretary, wu2014strategy}. The time-discounting property really complicates the mechanism design problem. For instance, it has been proved that no online algorithm can achieve a competitive ratio better than $\Omega(\textrm{log}n/\textrm{log}\,\textrm{log}n)$ for discounted secretary problem~\cite{babaioff2009secretary}. The time-discounting property of values will bring much more difficulty, especially on the strategy-proofness. In the most of the incentive mechanisms designed for online crowdsensing, the payment to a selected participant is based on her contributation. However, in the case with time-discounting values, the true contributation will be affected by more factors. For a participant, if she can cheat her type, such as arrival time or cost, she may be selected at different time. If this time is earlier than the time with truely report information, the value of this participant calculated by the platform will be higher than the true value. For the purpose of more reward, the participant may have more incentives to bid mendaciously.

@@

To address these challenges, we propose a budget feasible online incentive mechanism with time-discounting values. We first consider the case where the total value is the summation of each participant's value. We define the efficiency of a participant as her value divided by her cost. Since participants arrive dynamically, we take advantage of the efficiency information of those who have arrived (we call a sample set) to calculate a threshold, and use it to guide subsequent selections. The intuition of our design is to greedily choose participants with the highest efficiencies from the sample set, and calculate their average efficiency multiplying an increasing factor as a threshold. The increasing factor is used to prevent the participants from misreporting their arrival or departure time. We divide the total time into slots. At each time slot, we select participants with efficiencies higher than the threshold within the budget constraint, and then calculate their payments. The payment scheme is carefully designed to ensure strategy-proofness and individual rationality. We prove that our mechanism can achieve a constant competitive ratio compared with the optimal solution with full information. We next consider the case where the total value is a submodular function of the selected participants, which is a more general situation. We prove that the time and cost-truthfullness can still be guaranteed by the newly designed algorithms. The numerical results show that our proposed approach has superior performance to our benchmark mechanisms.
\subsection{Key Contributions}
The main contributions of this paper is listed as follows
\begin{itemize}
\item We design an online incentive mechanism for crowdsensing. In this process, participants arrive over time. Our mechanism is designed to take advange of their efficiency to select them and give them payments.

\item As far as we know, we are the first to consider the time-discounting property of values in the crowdsensing paradigm. To address the potential new difficulty, we design a novel algorithm to calcuate a time-related threshold to select participants and determine their payments.

\item We think about two cases according to the value function. The value function considered in these two cases is linear additive and submodular. The latter value function is more general.
\end{itemize}
\subsection{Paper Organization}
The rest of the paper is organized as follows. We briefly review the related work in Section II. In Section III, We introduce the model of the budget feasible online mechanism problem with time-discounting values, and recall some important solution concepts. In Section IV, we present our design of a strategy-proof online  mechanism where the value function is the summation of each participant's value. In Section V, we consider the case where the value function submodular. In Section VI, we implement and evaluate our mechanism. Finally, we conclude this paper in Section VII.
%**********************************************************
%The key challenges in a budget feasible auction are how to persue the maximum value and balance incentive compatibility and the budget constraint. It gets harder when the participants arrive dynamicly. What is noticeable is that in existing works, the value of a specific participant is often fixed, \ie, the participant has a bid of uniform value during her presence in the auction, independent of when she is selected. But in some realms, such as applications intending to collect data by crowdsensng, which are always modeled as reverse auctions, the values of participants' contributed information decrease with time. The time discounting characteristic can make the problem more difficult. In this paper, we study a type of online reverse auction, where the participants compete to provide items or services with certain time discounting values. Then the provider gives some payment to the selected participants according to their bids. The objective is to obtain  the maximum total value and achieve strategy-proofness under a limited budget. It should be noted that for general utility functions, there is no truthful mechanism achieving a reasonable approximation ratio~\cite{singer2014budget}. In our paper, the total value of participants is simplified to the summation of their values at when they are selected.
%**********************************************************
%We present a formal methonology based on the mechanism design as an inventive method in the realm of crowdsensing. which is a new paradigm of applications that includes a platform and ubiquitous participants who hold mobile devices equipped with enhanced sensors~\cite{ganti2011mobile}. The platform recruits participants to upload sensing data and then compensate them some payment according to their value. It is always modeled as a reverse auction. When designing an incentive mechanism for crowdsensing, participants' value is often taken into account when determining the task allocation and the payment. But in existing work, this value of a specific participant is often fixed, \ie, the participants have a bid of uniform value to the platform during their presences in the auction. However in many crowdsensing applications, the value of participants is time discounting, decreasing with time in majority situations. Therefore in this paper, we consider a scenario, in which participants compete for being allocated tasks and then compensated some monetary payment, but her bidding value is changing over time.  The bid of each participant is her arrival time, departure time, her cost and value to the platform which diminishes with time. The objective is to design a strategy-proof mechanism and maximize the platform's gainning value with limited budget with respect to not only the time discounting values, but also the present time and cost of the participants.

@@

In the case where the value of a participant has nothing to do with others', their total value is the summeration of each participant's. The type of each participant $i$ is $\theta_i=(a_i,d_i,v_i,c_i)$, where $a_i$ and $d_i$ represent her arrival and departure time respectively, $v_i$ denotes participant $i$'s value to the crowdsensing platform and $c_i$ represents her cost or reserve price in performing the sensing task. Here, reserve price is the minimum payment that a participant is willing to receive. In other words, each selected participant should get a payment no less than her reserve price. We note that $a_i$, $d_i$ and $c_i$ are participant $i$'s private information that are unknown to the service provider unless being reported, while $v_i$ is assumed to be $i$'s public information since participants' values can be known a prior or evaluated by the service provider \cite{peng2015pay,jin2015quality}. Upon participant $i$'s arrival, she will submit her bid $\hat{\theta}_i=(\hat{a}_i,\hat{d}_i,v_i,b_i)$ to the service provider. We note that since the participants are rational and selfish, they may cheat their arrival time, departure time, or reserve prices for the purpose of earning more payment or improving the possibility to be selected \cite{nisan2007algorithmic}, indicating that participant $i$'s bid may not be her true type. It is known that reporting earlier arrival or later departure can be prevented by heart-beat scheme~\cite{nisan2007algorithmic}, we focus on the scenario where each participant can only report an arrival time later than her true arrival time or a departure time earlier than her true departure time, \ie, $\hat{a}_i\ge a_i, \hat{d}_i\le d_i$. Participant $i$ can also misreport her reserve price $b_i \neq c_i$ to manipulate the participant selection process.

@@

\section{Mechanism Design}
We first consider the simpler case where the total value function is the summeration. In this section, we propose an online mechanism, which is named as TDM, satisfying the following properties:
\begin{itemize}
\item \textbf{Computational Efficiency}: Each step of the mechanism should be computed in polynomial time.

@@

\item \textbf{Competitive Ratio}: We define the competitive ratio as the ratio between the expected total value gained in our mechanism and the optimal value where this provider has full information of all participants~\cite{zhao2014crowdsource}. We will prove our mechanism can achieve a constant competitive ratio. In our proof, we ignore the effect of time-discounting property because it will only change the constant coefficient.
\end{itemize}

@@

\begin{algorithm}
\BlankLine
\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output}
\caption{Modified greedy algorithm}
\label{alg:greedy}
\begin{small}
\Input{Budget $B$, the participant set $\mathbb{P}=\{p_1,p_2,...,p_n\}$}
\Output{Selected Participants}
\BlankLine
$\mathbb{S}\rightarrow\emptyset,C\rightarrow 0,\mathbb{U}\rightarrow\mathbb{S}$;\\
\While{$\mathbb{U}\neq\emptyset$}{
	select $p_i \in \mathbb{U}$ that maximizes $\frac{v_i}{c_i}$;\\
	\If{$C+c_i\le B$}{
		$\mathbb{S}\rightarrow\mathbb{S}\cup{p_i}$;\\
		$C\rightarrow C+c_i$;\\
	}
	$\mathbb{U}\rightarrow\mathbb{U}\backslash\{p_i\}$;
}
Select a participant $p*$ that maximizes $v*$ over $\mathbb{P}$;\\
If $V(\mathbb{S})\ge v*$, output $\mathbb{S}$, otherwise, output $\{p*\}$;
\end{small}
\end{algorithm}

@@

When $\epsilon$ is sufficiently small, we can always find such a parameter $\lambda$ equals $2\left(\frac{U}{L}\right)^{l-1}$. Then the expected competitive ratio is:
\begin{align}
\left(\frac{U}{L}\right)^{2-2l}\frac{U}{16(U+L)}(1-\frac{1}{e}). 
\end{align}
\end{proof}
% Due to limitations of space, we omit the proof here.
%\begin{equation}
%\left\{
%\begin{aligned}
%\frac{\left(\frac{U}{L}\right)^{l-1}}{\lambda}<\frac{1}{2}\\
%\lambda < \frac{\left(\frac{U}{L}\right)^{l-2}}{\epsilon}\\
%\end{aligned}
%\right.
%\end{equation}
\section{Mechanism with Monotone Submodular Value Function}
In this section, we propose an online mechanism, which is named as TDMS, for the general model.
\subsection{System Model}
The general model is similar with the model we have presented in section III. However the task is divided into some sub-tasks and the bid of each participant includes the set of sub-tasks she can finish. The bid of of participant $i$ is $\theta_i=(a_i,d_i,p_i,c_i)$, where we use the same notation $p_i$ to represent the sub-task set of participant $p_i$ for brevity.
\subsection{Mechanism Design}
In last section, we propose an incentive mechanism for online crowdsensing with time-discounting values, specifically the total obtained value is a linear summeration of value contributed by each participant, \ie,
%\begin{small}
\begin{equation}
V=\sum\limits_{i \in \mathbb{S}}v_i(t_i)
\end{equation}
%\end{small}
However in many scenarios~\cite{zhao2014crowdsource}, the value of participants to the platform is $f(\mathbb{S})$, where $f$ is a monotone submodular function and $\mathbb{S}$ is the selected participants set. Particularly, we have solved the case where the value function $f(\mathbb{S})=\sum\limits_{i \in \mathbb{S}}v_i(t_i)$. Here we give the definition of monotone submodular function.
\begin{definition}[Monotone Submodular Function]
A function $f:2^{[n]}\to \mathbb{R}$ is submodular if and only if:
\begin{equation}
f(\mathbb{A}\cup\{i\})-f(\mathbb{A})\ge f(\mathbb{B}\cup \{i\})-f(\mathbb{B}). \quad \forall\ \mathbb{A}\subseteq\mathbb{B} \notag
\end{equation}
\end{definition}
In existing works focused on submodular function maximation in the realm of incentive mechanism design for crowdsensing, the marginal value contributed by a participant is related to the order she is selected. Besides, the total value is only decided by the tasks of the selected participants. However in this paper, considering the time-discounting property, the value function is a bit more complicated. We still use the notation $f$ to denote the value function without considering time-discounting value. When a participant $i$ is selected at time $t_i$, her marginal contribution given a subset $\mathbb{S}$ is $f_{i|\mathbb{S}}=(f(\mathbb{S}\cup\{i\})-f(\mathbb{S}))\times\beta ^{-t_i}$.
Assume the selected participant set is $\{i_1,i_2,...,i_n\}$ and their selected time is $t_{i_1},t_{i_2},...,t_{i_n}$ respectively. So when selecting the first participant $i_1$, her real contribution value is $f_{t_{i_1}}(\{i_1\})=f(\{i_1\})\times \beta^{-t_{i_1}}$. The value contributed by the secondly selected participant without consider time-discounting property is $f(\{i_1,i_2\})-f(\{i_1\})$ and her true contribution should be discounted by timing $\beta^{t_{i_2}}$. Thus, the total value contributed these two participants is $f_{t_{i_1},t_{i_2}}(\{i_1,i_2\}) = f_{t_{i_1}}(\{i_1\})\times \beta^{-t_{i_1}} + [f(\{i_1,i_2\})-f(\{i_1\})]\times\beta^{-t_{i_1}}$. We use $\tilde{f}$ to substitute $f$ when considering time-discounting property. So, the total value contributed by all these $n$ participants are
\begin{align}
&\tilde{f}(\{i_1,i_2,...,i_n\}) = f_{t_{i_1},t_{i_2},...,t_{i_n}}(\{i_1,i_2,...,i_n\}) \notag \\
&=f_{t_{i_1}}(\{i_1\})\times \beta^{-t_{i_1}} + [f(\{i_1,i_2\})-f(\{i_1\})]\times\beta^{-t_{i_1}} \notag\\
&+... +[f(\{i_1,i_2,...,i_{n}\})-f(\{i_1,i_2,...,i_{n-1}\})]\times\beta^{-t_{i_n}} 
\end{align}

\begin{theorem}
The new total value function $\tilde{f}$ with time-discounting value is still monotone submodular.
\end{theorem}
\begin{proof}
We can prove this according to the definition of submodular function.

@@

We denote participant $i$'s marginal contribution given a subset $\mathbb{A}$ as
 $\tilde{f}^i_{t_i}(\mathbb{A}) = [f(\mathbb{A}\cup\{i\}) - f(\mathbb{A})]\times \beta^{-t_i}$.
Next we modify the procedure to calculate the threshold when the value function is submodular. Recall that we assume $L\le\frac{v}{b}\le U$ before, here we make a reasonable assumption that $L\le\frac{f^i(\emptyset)}{b_i}\le U$. Then we also can infer that $L\le\frac{f^i(\mathbb{A})}{b_i}\le U$ for all set $\mathbb{A}$.

@@

Next we propose the participant selection algorithm(Alg. 5) as before. We should pay more attention to the truthfulness. Since the value function is submodular, the marginal distribution is related to a given subset. If the order of selection is changed, the marginal distribution will change as well. This is a new kind of opportunity for the participants to cheat her bids. Singer has ever studied a budget mechanism~\cite{singer2010budget}, where the value function is submodular. However it is used in offline scenario, we will give an online version.
